Experience-Biased Symbolic Planning

### 2014-05-12 AAAI_AuthorKit/paper.tex
ComputeG

\begin{algorithm}
\caption{ComputeG($S$)}
\label{alg:ComputeG}
\begin{algorithmic}
\FORALL{$a \in A$}
\IF{$a \in S$}
\STATE $g_S(a) \leftarrow 0$
\ELSE
\STATE $g_S(a) \leftarrow \infty$
\ENDIF
\ENDFOR
\REPEAT
\FORALL{$op \in O$}
\STATE $pCost \leftarrow g_S(Prec(op))$
\FORALL{$a \in Add(op)$}
\STATE $g_S(a) \leftarrow \min \left(g_S(a),~pCost + Cost(op)\right)$
\ENDFOR
\ENDFOR
\UNTIL{no further change in $g_S$-values}
\end{algorithmic}
\end{algorithm}

@@

\[h^E(S_0) = \min_{N,S_N,\pi} \sum_{i=1}^N \min \{\epsilon^E h(S_{i-1},S_i),c^E(S_{i-1},S_i)\}\]
over all goal states $S_N$ and paths $\pi = \langle S_0,S_1,...,S_N \rangle$.

$c^E$ are E-graph edge costs, or $\infty$ if the E-graph edge does not exist.

>>>>

\begin{algorithm}
\caption{ComputeG($S$)}
\label{alg:ComputeG}
\begin{algorithmic}
\FORALL{$a \in A$}
\IF{$a \in S$}
\STATE $g_S(a) \leftarrow 0$
\ELSE
\STATE $g_S(a) \leftarrow \infty$
\ENDIF
\ENDFOR
\REPEAT
\FORALL{$op \in O$}
\STATE $cost\_estimate \leftarrow g_S(Prec(op)) + Cost(op)$
\FORALL{$a \in Add(op)$}
\STATE $g_S(a) \leftarrow \min \left(g_S(a),~cost\_estimate\right)$
\ENDFOR
\ENDFOR
\UNTIL{no further change in $g_S$-values}
\end{algorithmic}
\end{algorithm}

@@

\[h^E(S_0) = \min_{N,S_N,\pi} \sum_{i=1}^N \min \{\epsilon^E h(S_{i-1},S_i),c^E(S_{i-1},S_i)\}\]
with the minimization taking place over all goal states $S_N$ and paths $\pi = \langle S_0,S_1,...,S_N \rangle$. $c^E$ are E-graph edge costs, or $\infty$ if the E-graph edge does not exist.
